A Large-Scale Study of the Use of Eval in R

### 2020-08-22 inst/paper/main.tex
intro

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above, R is a lazy language, like Haskell, the authors have informally
  surveyed end-users, some of them computer scientists, and did not find a
  single one aware of that fact. Library developers, on the other hand, tend
  to know about laziness and program defensively around it.} Thus, our
corpus distinguished between ,....

This paper looks at eval in the context of data science. We look at the use
of eval in the R programming language. And in particular we look at its use
in three different contexts.  The first context is the implementation of the
language, how is eval used by the core developers of R in the packages that
are part of the R virtual machine.  The secoond context is how it is used in
libraries. And the third context is how it is used by end users of the
language.

>>>>

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above consider that R uses lazy evaluation like Haskell. The authors
  have informally surveyed end-users, some of them computer scientists, and
  did not find a single one aware of that fact. Library developers, on the
  other hand, tend to know about laziness and program defensively around
  it.}  Thus, our corpus distinguished between \emph{core packages} (there
are \miss{8} such packages that are loaded together with the R virtual
machine), \emph{CRAN packages} (these are curated packages that pass
stringent community quality checks and are equipped with tests and sample
data), \emph{scripts} (end-user written code that performs a particular
machine learning or data analysis task).
